Talks

### 2025-05-12 talks.qmd
update

>>>>

- June 4. Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.

- Panel on Distributed Peer Review, International Conference on the Science of Science ([ICSSI](https://icssi.org/)), June 16 - 18, Copenhagen.

- Evaluating Distributed Peer Review at the Volkswagen Foundation. Metascience 2025, June 30 - 2 July, London.

- Can AI be used for better matching of proposals to reviewers? Feasibility and formal evaluation with the Metascience 2025 conference. Metascience 2025, June 30 - 2 July, London.

## 2025

- 25 March: The Accelerator For Innovation & Research Funding Experimentation - AFIRE @ The National Research Foundation, South Africa; and Research on Research Institute Partnership Meeting: [slides](https://docs.google.com/presentation/d/1UkmQxS7nlKJA784B95NuNO_UoH6PlDl6/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)

- 19 February: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1E_A9yS-zeZNSJ7M41t8g2l9U_5ObDcc3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
